Clean 2015 Raw Data

### 2018-04-29 data-raw/README.Rmd
Remove TRT from data
The interaction of irrigation and N management are not analysed. remove from data

  x <- dplyr::arrange(x, REP, TRT)

@@

  TShB_incidence <-
    x %>% dplyr::select(REP,
                        TRT,
                        WMGT,
                        NRTE,
                        SMPL,
                        HILL,
                        HGHT,
                        NTIL,
                        NTShB,
                        TShB_incidence)

@@

  for (i in 1:4) {
    y <-
      x %>%
      dplyr::select(
        TRT,
        REP,
        WMGT,
        SMPL,
        NRTE,
        HILL,
        paste0("TIL", i),
        paste0("GL", i),
        paste0("DL", i),
        paste0("SHB", i),
        paste0("SLA", i),
        paste0("SLB", i),
        paste0("SLC", i),
        paste0("SLD", i),
        paste0("SLE", i),
        paste0("SLF", i)
      ) %>%
      tidyr::gather(LEAF,
                    LEAF_ShB,
                    dplyr::starts_with("SL"))

    names(y)[7] <- "TIL"
    names(y)[8] <- "GL"
    names(y)[9] <- "DL"
    names(y)[10] <- "TIL_ShB"

@@

# Add treatment numbers --------------------------------------------------------
DS2015$TRT <- NA
DS2015$TRT[which(DS2015$WMGT == "FLD" &
                   DS2015$NRTE == 0)] = "FLD_N0"
DS2015$TRT[which(DS2015$WMGT == "FLD" &
                   DS2015$NRTE == 100)] = "FLD_N100"
DS2015$TRT[which(DS2015$WMGT == "FLD" &
                   DS2015$NRTE == 120)] = "FLD_N120"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 0)] = "AWD_N0"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 100)] = "AWD_N100"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 120)] = "AWD_N120"

@@

# Arrange columns --------------------------------------------------------------
DS2015 <-
  DS2015 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

@@

```{r}
# Preprocess 2016 data for all assessments
#
# 1. Cleanup date format and fill empty dates
# 2. Fill empty NTIL (for same hill, not missing values)
# 3. Fill empty NTShB (for same hill, not missing values)
# 4. Add column with number of days after inoculation (DAI)

@@

# Add treatment numbers --------------------------------------------------------
DS2016$TRT <- NA
DS2016$TRT[which(DS2016$WMGT == "FLD" &
                   DS2016$NRTE == 60)] = "FLD_N60"
DS2016$TRT[which(DS2016$WMGT == "FLD" &
                   DS2016$NRTE == 180)] = "FLD_N180"
DS2016$TRT[which(DS2016$WMGT == "AWD" &
                   DS2016$NRTE == 60)] = "AWD_N60"
DS2016$TRT[which(DS2016$WMGT == "AWD" &
                   DS2016$NRTE == 180)] = "AWD_N180"

DS2016 <-
  DS2016 %>%
  tidyr::gather(
    LEAF,
    LEAF_ShB,
    dplyr::starts_with("ShBL"),
    -DATE,
    -ASMT,
    -DAI,
    -PLOT,
    -TRT,
    -REP,
    -WMGT,
    -SMPL,
    -NRTE,
    -HILL,
    -NTIL,
    -GL,
    -DL,
    -NTShB,
    -NSHShB,
    -TIL
  )

@@

# calculate tiller sheath blight incidence
DS2016 <-
  DS2016 %>%
  dplyr::group_by(DATE, ASMT, DAI, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
  dplyr::mutate(TShB_incidence = NTShB / NTIL)

@@

DS2016 <-
  DS2016 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

@@

# Arrange columns --------------------------------------------------------------
DS2016 <-
  DS2016 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE,
    DAYS
  )
```

@@

# convert columns to factor ----------------------------------------------------
RAW_data$YEAR <- factor(RAW_data$YEAR)
RAW_data$ASMT <- factor(RAW_data$ASMT)
RAW_data$PLOT <- factor(RAW_data$PLOT)
RAW_data$REP <- factor(RAW_data$REP)
RAW_data$TRT <- factor(RAW_data$TRT)
RAW_data$WMGT <- factor(RAW_data$WMGT)
RAW_data$NRTE <- factor(RAW_data$NRTE)
RAW_data$SMPL <- factor(RAW_data$SMPL)
RAW_data$HILL <- factor(RAW_data$HILL)
RAW_data$TIL <- factor(RAW_data$TIL)
RAW_data$LEAF <- factor(RAW_data$LEAF)

@@

RAW_data$TRT <-
  forcats::fct_relevel(
    RAW_data$TRT,
    "AWD_N0",
    "AWD_N100",
    "AWD_N120",
    "AWD_N60",
    "AWD_N180",
    "FLD_N0",
    "FLD_N100",
    "FLD_N120",
    "FLD_N60",
    "FLD_N180"
  )

@@

# 2015 Tiller incidence setup --------------------------------------------------
TShB_inc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  dplyr::arrange(PLOT)

@@

# 2015 Tiller Severity AUDPS ---------------------------------------------------
TShB_sev_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_perc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

# 2015 Leaf Severity setup -----------------------------------------------------
LShB_sev_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

LShB_perc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:6],
                   dates = dplyr::pull(TShB_inc_15[1:5, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:6],
                   dates = dplyr::pull(TShB_sev_15[1:5, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
                   dates = dplyr::pull(LShB_sev_15[1:5, 6]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
        dates = dplyr::pull(TShB_perc_15[1:5, 6]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
        dates = dplyr::pull(LShB_perc_15[1:5, 6]))

@@

# 2016 Tiller Incidence setup --------------------------------------------------
TShB_inc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  dplyr::arrange(PLOT)

@@

TShB_sev_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

LShB_sev_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

LShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:5],
                   dates = dplyr::pull(TShB_inc_16[1:4, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:5],
                   dates = dplyr::pull(TShB_sev_16[1:4, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:5],
                   dates = dplyr::pull(LShB_sev_16[1:4, 6]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:5],
                   dates = dplyr::pull(TShB_perc_16[1:4, 6]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:5],
                   dates = dplyr::pull(LShB_perc_16[1:4, 6]))

@@

# Merge AUDPS data for graphing ------------------------------------------------
AUDPS <- tibble::as_data_frame(tibble::as_tibble(rbind(ShB_15, ShB_16)))
AUDPS <- tidyr::separate(data = AUDPS, col = TRT,
                         sep = "_",
                         into = c("WMGT", "NRTE"))
AUDPS <- dplyr::mutate_at(.tbl = AUDPS,
                              .funs = factor,
                              .vars = c("WMGT", "NRTE"))

@@

row.names(N_rates) <- c("N0", "N100", "N120", "N60", "N180")

>>>>

  x <- dplyr::arrange(x, REP, WMGT, NRTE)

@@

  TShB_incidence <-
    x %>% dplyr::select(REP,
                        WMGT,
                        NRTE,
                        SMPL,
                        HILL,
                        HGHT,
                        NTIL,
                        NTShB,
                        TShB_incidence)

@@

  for (i in 1:4) {
    y <-
      x %>%
      dplyr::select(
        REP,
        WMGT,
        SMPL,
        NRTE,
        HILL,
        paste0("TIL", i),
        paste0("GL", i),
        paste0("DL", i),
        paste0("SHB", i),
        paste0("SLA", i),
        paste0("SLB", i),
        paste0("SLC", i),
        paste0("SLD", i),
        paste0("SLE", i),
        paste0("SLF", i)
      ) %>%
      tidyr::gather(LEAF,
                    LEAF_ShB,
                    dplyr::starts_with("SL"))

    names(y)[6] <- "TIL"
    names(y)[7] <- "GL"
    names(y)[8] <- "DL"
    names(y)[9] <- "TIL_ShB"

@@

@@

# Arrange columns --------------------------------------------------------------
DS2015 <-
  DS2015 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

@@

# Preprocess 2016 data for all assessments
#
# 1. Cleanup date format and fill empty dates
# 2. Fill empty NTIL (for same hill, not missing values)
# 3. Fill empty NTShB (for same hill, not missing values)
# 4. Add column with number of days after inoculation (DAI)

@@

DS2016 <-
  DS2016 %>%
  tidyr::gather(
    LEAF,
    LEAF_ShB,
    dplyr::starts_with("ShBL"),
    -DATE,
    -ASMT,
    -DAI,
    -PLOT,
    -REP,
    -WMGT,
    -SMPL,
    -NRTE,
    -HILL,
    -NTIL,
    -GL,
    -DL,
    -NTShB,
    -NSHShB,
    -TIL
  )

@@

# calculate tiller sheath blight incidence
DS2016 <-
  DS2016 %>%
  dplyr::group_by(DATE, ASMT, DAI, REP, PLOT, WMGT, NRTE, SMPL, HILL) %>%
  dplyr::mutate(TShB_incidence = NTShB / NTIL)

@@

DS2016 <-
  DS2016 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

@@

# Arrange columns --------------------------------------------------------------
DS2016 <-
  DS2016 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    DAI,
    REP,
    PLOT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE,
    DAYS
  )
```

@@

# convert columns to factor ----------------------------------------------------
RAW_data$YEAR <- factor(RAW_data$YEAR)
RAW_data$ASMT <- factor(RAW_data$ASMT)
RAW_data$PLOT <- factor(RAW_data$PLOT)
RAW_data$REP <- factor(RAW_data$REP)
RAW_data$WMGT <- factor(RAW_data$WMGT)
RAW_data$NRTE <- factor(RAW_data$NRTE)
RAW_data$SMPL <- factor(RAW_data$SMPL)
RAW_data$HILL <- factor(RAW_data$HILL)
RAW_data$TIL <- factor(RAW_data$TIL)
RAW_data$LEAF <- factor(RAW_data$LEAF)

@@

RAW_data$WMGT <-
  forcats::fct_relevel(
    RAW_data$WMGT,
    "AWD",
    "FLD"
  )

@@

# 2015 Tiller incidence setup --------------------------------------------------
TShB_inc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  dplyr::arrange(PLOT)

@@

# 2015 Tiller Severity AUDPS ---------------------------------------------------
TShB_sev_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_perc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

# 2015 Leaf Severity setup -----------------------------------------------------
LShB_sev_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

LShB_perc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:6],
                   dates = dplyr::pull(TShB_inc_15[1:5, 8]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:6],
                   dates = dplyr::pull(TShB_sev_15[1:5, 8]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
                   dates = dplyr::pull(LShB_sev_15[1:5, 8]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
        dates = dplyr::pull(TShB_perc_15[1:5, 8]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
        dates = dplyr::pull(LShB_perc_15[1:5, 8]))

@@

# 2016 Tiller Incidence setup --------------------------------------------------
TShB_inc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  dplyr::arrange(PLOT)

@@

TShB_sev_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  dplyr::arrange(PLOT)

@@

LShB_sev_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

LShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

@@

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:5],
                   dates = dplyr::pull(TShB_inc_16[1:4, 8]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:5],
                   dates = dplyr::pull(TShB_sev_16[1:4, 8]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:5],
                   dates = dplyr::pull(LShB_sev_16[1:4, 8]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:5],
                   dates = dplyr::pull(TShB_perc_16[1:4, 8]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:5],
                   dates = dplyr::pull(LShB_perc_16[1:4, 8]))

@@

# Merge AUDPS data for graphing ------------------------------------------------
AUDPS <- tibble::as_data_frame(tibble::as_tibble(rbind(ShB_15, ShB_16)))

# Arrange NRTE values
AUDPS$NRTE <-
  forcats::fct_relevel(AUDPS$NRTE,
                       "0",
                       "100",
                       "120",
                       "60",
                       "180")

@@

row.names(N_rates) <- c("0", "100", "120", "60", "180")
